Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-20 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides by conducting an experiment comparing with promising QoS-aware model. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, and compare the PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.

@@

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. but there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution. These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured by the quality of semantic links that requires formal definition of ontology in Description Logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches. There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a POS-based method with explicit support for the comprehensive model to find optimal compositions.

@@

The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request. The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above. A motivating example of this problem is shown in Fig \ref{motivation}. The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning problem from scholars who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city. The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.

@@

Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services in a service repository. These web services have different QoS (such as availability, price, reliability and response time ). Moreover, the valid semantic matches between two web services could be associated with different semantic matchmaking quality. For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap required by users. Fig .\ref{taxonomy} represents a taxonomy of all the inputs and  the outputs described in Fig. \ref{motivation} for a travel planning domain, where the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively. The valid semantic match is considered that an instance of urban Map must be an instance of Map, not vice versa. If a web service $GenerateTouristMap$ found in the service repository that produces TouristMap as an output. I consider its semantic matchmaking quality is higher than that of $GenerateMap$. However, $GenerateTouristMap$ might have a very bad QoS.

@@

We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model.
\vspace{0.3cm}

\textbf{Semantic Web Service Model}. The semantic web service model represent web services with functional descriptions, and how interoperability of web services enable matchmaking to automatically generate composition solutions.

@@

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a set of $S$, where all the $S$ are registered.
\vspace{0.3cm}

\textbf{Semantic Matchmaking Model}. The mechanism to compose web services relays on the semantic inputs and outputs, which enable inputs to be matched by outputs. To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ) into consideration for exploiting the semantics of inputs and outputs.

@@

\textbf{QoS Model in a Weighted DAG}
Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service. \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame. \textit{Availability} ($A$) is the probability that a web service is accessible.

	The aggregation value of QoS in a DAG with respect to different constructs, which reflects how services associated with each other in a service composition. Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service. The QoS calculation models are described as follows:

\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.

@@

$\forall WG^{'}$ , $q(a \Rightarrow b) \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq q(a \Rightarrow b) \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model. We compare this model with a promising QoS-aware model, and also compare our PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.

@@

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of a graph is minimised to reach the optimised graph-based composition solutions. However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. but there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.

Few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic. This evaluation method takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured by the similarity using information retrieval technique.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches. There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a PSO-based method with explicit support for the comprehensive model to find optimal compositions.

@@

The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request. The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above. A motivating example of this problem is shown in Fig \ref{motivation}. The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning problem for scholars who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city. The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.

@@

Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services from a service repository. These web services have different QoS in terms of different availability, price, reliability and response time. Moreover, valid semantic matches between two web services could also have different matchmaking quality. For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap from users' perspectives. These perspectives are captured in a taxonomy Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning domain. For example, the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of urban Map can be an instance of Map, but not vice versa. However, if a web service $GenerateTouristMap$ is found in the service repository that produces TouristMap as an output, but price is "16.87". I consider its semantic matchmaking quality is higher than the service $GenerateMap$, but price negatively contributes to the overall QoS. Therefore, automatically generating solutions in considering both QoS and matchmaking quality is a very challenging problem.

@@

We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of four main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
\vspace{0.3cm}

\textbf{Semantic Web Service Model}. The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.

@@

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$, where all the $S$ are registered.
\vspace{0.3cm}

\textbf{Semantic Matchmaking Model}. The mechanism to compose web services relays on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another. To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ) into consideration for exploiting the semantics of inputs and outputs.

@@

\textbf{QoS Model in a Weighted DAG}
Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service. \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame. \textit{Availability} ($A$) is the probability that a web service is accessible. The aggregation value of QoS in a DAG respect to the structures of DAG, which reflects how services associated with each other in a service composition. The QoS calculation models are described as follows:

\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned defined as :
$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.

\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned defined as :
$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.

\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned defined as :
$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.

@@

$\forall WG^{'}$ , $\{q(a \Rightarrow b) \} \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq \{ q(a \Rightarrow b) \} \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $
